---
title: "p8105_hw1_yf2735"
author: "Yujing FU"
date: "2024-09-18"
output: github_document
---
```{r setup, echo = FALSE, message = FALSE} 
library(ggplot2)
library(tidyverse)
```
## problem 1
```{r}
data("penguins", package = "palmerpenguins")
```
The data in this dataset is showed as follows:
```{r}
penguins
```
The dataset has 344 rows and 8 columns.
```{r}
print(paste("row =", nrow(penguins)))
print(paste("col =", ncol(penguins)))
```
The mean of the flipper length is around 200 mm
```{r}
print(paste("mean_flipper_length =", mean(penguins$flipper_length_mm, na.rm = TRUE)))
```
The scatterplot of flipper_length_mm (y) vs bill_length_mm (x):
```{r}
penguins_clean <- na.omit(penguins)
ggplot(data=penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(title = "Scatterplot of Flipper Length VS Bill Length",
       x = "bill length (mm)",
       y = "flipper length (mm)")
ggsave("scatterplot_flipper_vs_bill_length.png")
```

## problem 2
```{r}
set.seed(111)
hw1_df = tibble(
  vec_numeric = rnorm(10, mean = 0, sd = 1),
  vec_logical = vec_numeric > 0,
  vec_char = letters[1:10],  
  vec_factor = factor(rep(1:3, length.out = 10), labels = c("level 1", "level 2", "level 3"))
)
hw1_df
```
To compute their means:
```{r}
set.seed(111)
mean(pull(hw1_df, vec_numeric))  
mean(pull(hw1_df, vec_logical))  
mean(pull(hw1_df, vec_char))
mean(pull(hw1_df, vec_factor))   
```
Summarize:

1) numerical caribles can work

2) logical varibles will be automatically transferred to 0 or 1, therefore the mean can be computed

3) character variables can't work because we can't take the mean of some characters

4) factor variables can't work because they can't be averaged directly

To convert variables from one type to another:
```{r, results = 'hide'}
as.numeric(pull(hw1_df, vec_logical))
as.numeric(pull(hw1_df, vec_char))
as.numeric(pull(hw1_df, vec_factor))
```

